A Reimplementation of Python's dict using Simple Tabulation Hashing and Linear Probing

### 2013-04-22 docs/paper_lncs.tex
Add in machine information
New abstract

\begin{abstract}
Here we implement simple tabulation hashing with linear probing in Python
dictionary based on the recent theoretical result of P\v{a}tra\c{s}cu et al. Although
we achieved significant performance wins on synthetic benchmarks, on real
benchmarks our wins were only on the order of 4\% due to interpreter overhead.
Linear probing with simple tabulation hashing does improve Python performance
and should be looked at as a replacement scheme.  As a whole, the
extra memory bandwidth
and latency required to compute the tabulation hash negates some of the
performance improvements, but if they were able to be further mitigated, the new scheme
should provide more than a 4\% improvement, making it even more worthwhile.
\keywords{Hash Function, Simple Tabulation, Linear Probing, Python Dictionary}
\end{abstract}

@@

In order to analyze the result of this new dictionary we measured three main
metrics. First, we compared the performance of the simple tabulation hashing
with Python's current hashing scheme on random and sequential strings. Second, we measured the number of probes and collisions and overall the quality of our dictionary on structured and unstructured inputs. Finally, in this section  we show some of the total time spent in dictionary operations by using a set of general Python benchmarks and some real-world programs.
\subsection{Table Number Tuning}

>>>>

\begin{abstract}
We reimplement the Python dictionary using simple tabulation hashing with linear probing based on the recent theoretical result of P\v{a}tra\c{s}cu et al. This hashing scheme provides expected constant time per operation in theory and we analyze its performance in practice compared to existing schemes.
Our new implementation of Python's \textbf{dict} achieves significant performance wins on synthetic benchmarks.  
Overall Python performance on real world benchmarks improves by about 4\%.
Using linear probing with simple tabulation hashing does improve Python performance
and should be looked at as a replacement scheme.  As a whole, the
extra memory bandwidth
and latency required to compute the tabulation hash negates some of the
performance improvements, but if they were able to be further mitigated, the new scheme
should provide more than a 4\% improvement, making it even more worthwhile.
\keywords{Hash Function, Simple Tabulation, Linear Probing, Python Dictionary}
\end{abstract}

@@

In order to analyze the result of this new dictionary we measured three main
metrics. First, we compared the performance of the simple tabulation hashing
with Python's current hashing scheme on random and sequential strings. Second, we measured the number of probes and collisions and overall the quality of our dictionary on structured and unstructured inputs. Finally, in this section  we show some of the total time spent in dictionary operations by using a set of general Python benchmarks and some real-world programs.  We ran the following on an Intel Core 2 Duo P8400 processor (3M cache, 2.26GHz) w/ 4GB of 1066MHz DDR3 RAM.
\subsection{Table Number Tuning}
